DNA meth and IVF

### 2023-12-19 figs/art_example.Rmd
art example

mt <- head(mtable,30)
rownames(mt) <- mt$set
mt <- mt[,c("Estill 450k","Novakovic EPIC")]
rownames(mt) <- gsub("REACTOME_","",rownames(mt))
rownames(mt) <- gsub("_"," ",rownames(mt))
colfunc <- colorRampPalette(c("blue", "white", "red"))
heatmap.2(as.matrix(mt),scale="none",trace="none",margins=c(6,25),col=colfunc(25),cexRow=0.6,cexCol=1)

>>>>

mt <- head(mtable,30)
rownames(mt) <- mt$set
mt <- mt[,c("s.Estill","s.Novakovic")]
rownames(mt) <- gsub("REACTOME_","",rownames(mt))
rownames(mt) <- gsub("_"," ",rownames(mt))
colfunc <- colorRampPalette(c("blue", "white", "red"))
heatmap.2(as.matrix(mt),scale="none",trace="none",margins=c(6,25),col=colfunc(25),cexRow=0.6,cexCol=1)
